% TODO: MIT LICENSE
% Feel free to use this resume as a template.

\documentclass[letter,10pt]{dresume}
\begin{document}

\pagestyle{empty} % non-numbered pages

% TITLE
\dheader

% Work
\begin{sblock}{Work Experience}
  \experience%
    {8/2018.}{current}%
    {PhD Student}%
    {Johns Hopkins, Baltimore}

    \item Actively contributed towards grant proposal writing.
    \item Spearheading investigations into simulating partial dislocation in FCC
      metals to capture previously undescribed phenomenon in super alloy
      deformation.
    \item Developing Neural Nets as feature extractors for materials
      characterization.
    \item Bringing Material Science into the big data domain.
  \endexperience

  \experience%
    {7/2017.}{7/2018}%
    {Software Engineer}%
    {Google, Mountain View}

    \item Worked on Ray Kurzweil's team for Natural Language Understanding.
    \item Pioneered method for debiasing word, sentence and semantic vectors.
    \item Contributed towards internal framework for multi-tower semantic models
      (Universal Encoder).
    \item Worked with high dimension semantic location to extract valuable
      market information.
    \item Build massively parallel data processing pipelines for Google scale
      analysis (C++, MapReduce).
    \item Created and train machine learning Tensorflow graphs to deploy at
      scale.
    \item Created hyperparameter autotuning procedures for blackbox
      optimization.
  \endexperience

  \experience%
    {1/2015.}{5/2017}%
    {Undergraduate Researcher}%
    {Integrated Material Assessment \& Predictive Simulation Laboratory (USC)}

    \item Developed code for \$775,072 NASA grant (15540-FD03).
    \item Prototyped CAD-to-pointcloud meshing procedure specific for under
      independently awarded \$3,000 SURF grant.
    \item Integrated CUDA GPU processing in point-cloud meshing procedures.
    \item Designed a cochlea inspired piezoelectric energy harvester from
      co-authored \$3,000 Magellan Grant.
    \item Worked with acousto-elastic metamaterials- leading to publication.
  \endexperience

  \experience%
    {6/2016.}{8/2016.}%
    {Research and Development Intern}%
    {NASA Langley Research Center}

      \item Developing custom DPSML simulation software (C++) to run on
        massively parallel super computer (using MPI) clusters.
      \item Constructed laser excitation system to create guided waves in
        damaged composites for NDE observation.
      \item Automated operated experimental setup with vibrometer and laser
        using IO serial commands in C\#.
  \endexperience

  \experience%
    {5/2014.}{12/2015.}%
    {Co-founder/ Software Developer}%
    {CloudCollege PBC.}

      \item Collaborated to build the CloudCollege product which has secured
        \$50,000 in seed funding.
      \item Expanded and improved an existing beta product into a consumer-ready release.
      \item Coordinated business goals and product development.
      \item Ran user research studies in order to inform product direction.
  \endexperience

  \clearpage\\

  \experience%
    {9/2013.}{5/2016.}%
    {Undergraduate Researcher}%
    {Advanced Manufacturing Research Laboratory (USC)}

      \item Fabricated test molds for new method of spin mold processing using 3D printing.
      \item Used circuit boards and Arduinos to create controllable environment
        for spin processing.
      \item Wrote Ruby modules for Sketchup to help with design process.
  \endexperience

  \experience%
    {3/2013.}{9/2013.}%
    {Software Developer}%
    {BoomTown LLC.}

    \item Full time employee with a competitive salary at the age of 18.
    \item Extended and contributed to C\# API for over 600 frontend websites.
    \item Managed front-end websites in PHP (Later Hack as we experimented with
      HHVM), Less and Coffeescript.
  \endexperience

  \experience%
    {9/2012.}{3/2013.}%
    {Software Developer}%
    {Equiscript LLC.}

      \item Managed large amounts of business data between Salesforce platform,
        dedicated SQL servers and 3rd party stake holders.
      \item Wrote workflows and entire processes in Salesforce’s Apex (very
        similar to Java).
      \item Worked with C\#’s Linq library for detailed data processes.
      \item Developed in SQL, and Python automated data processing procedures.
      \item Provided elastic instance system administration on Amazon’s EC2
        platform, and Rackspace.
  \endexperience

\end{sblock}

%Section: Pubs
\begin{sblock}{Publications}
  \pub%
    {9/2016.}%
    {Journal of Intelligent Materials Systems and Structures}%
    {A process to Scavenge energy at low acoustic frequencies ($<$ KHz) with
    controlled geometric configurations (Ahmed, Madisetti, Banerjee)}
\end{sblock}

%Section: Honors
\hblock{Honors}
  \h%
    {2018.}{2nd Place HopHacks (MLH)}%
    {2017.}{NSF GRFP}

  \h%
    {2017.}{USC President of ASME}%
    {2017.}{Outstanding Senior Award}

  \h%
    {2017.}{USC Cyber Security Executive Staff}%
    {2016.}{SURF Grant Recipient}

  \h%
    {2015.}{Goldwater Fellowship Finalist}%
    {2015.}{Magellan Grant Recipient}

  \h%
    {2015.}{NSPE Foundation Scholarship}%
    {2014.}{Phi Beta Kappa Freshman Award}

  \h%
    {2015}{Tau Beta Pi}%
    {}{}

\endhblock

\end{document}
